---
title: "BellaBeat Case Study"
author: "Dominic Igwebuike"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
---

# Case Study of BellaBeats, A Fitness Brand That Serves Women.

## 1. INTRODUCTION

Bellabeat is a tech company that makes smart wearable gadgets.

They have a product catalogue of smart devices which function by collecting key user-data including, activity, sleep, stress, reproductive health, etc., to empower women with knowledge about their daily habits and inform them on their health lifestyles.

This case study focuses on the analysis of the user data generated by the fitness smart devices to see how it can help Bellabeat become smarter in their marketing, messaging, and maximize growth opportunities in the fitness industry.

This Case Study is completed as part of my Google Data Analytics Professional Capstone projects and i will be working with the R programming languge for this analysis.

The outcome of this analysis will help Bellabeat gain more insights on how consumers use smart devices and apps and this will help Bellabeat develop new on-demand features for their flagship Bellabeat App.

Bellabeat App is a consumer-centric app which provides users with health lifestyle data that covers activity, sleep, stress, menstrual cycle, and mindfullness habits. The Bellabeat App pulls and aggregate these data from the wearable smart devices that their customers use.

## 2. BUSINESS TASK AND STAKEHOLDERS

My task is to uncover trends on how consumers use non-bellabeat smart devices. The idea is to transfer these uncovered trends and insights to similar Bellabeat products and use them to inform Bellabeats marketing strategy.

**Stakeholders:**

Our stakeholders include:

1.  Urska Srsen

Ursen is Bellabeat cofounder and chief creative officer.

2.  Sando Mur

Sando is a cofounder of Bellabeat and a key member of Bellabeat executive team

3.  Bellabeat Marketing Analytics

Team who would be directly using and implementing the insights generated from this study.

## 3. ABOUT THE DATASET FOR THIS STUDY

We are using the publicly available Fitbit Fitness Tracker which is gathered from Kaggle.com. Thanks to the Morbius team for putting it up.

## 4. DATA PROCESSING AND ANALYSIS

We are going to be using these list of R packages for our analysis.

-   **tidyverse:** this includes dplyr for data wrangling, tidyr for tidying data, and ggplot2 for data visualization

-   **janitor:** for data cleaning and tidying, contains functions for column name cleaning, duplicate rows removal, handling missing data, etc

-   **lubridate:** for working with date and time data

-   **skimr**: for summarizing data

-   **ggrepel:** extends the capabilities of ggplot2 in making data points cleaner and removing overlaps

-   **ggpubr:** extends the abilities of ggplot2 to create multiple plots, etc.

## INSTALLATION OF R PACKAGES

```{r}

# code to make all my packages install properly

options(repos = "https://cran.r-project.org")
```

```{r}
# we begin installation of the R packages

install.packages('tidyverse')
```

```{r}
install.packages('janitor')
```

```{r}
install.packages('lubridate')
```

```{r}
install.packages('skimr')
install.packages('ggrepel')
install.packages('ggpubr')

```

Now that all the packages are installed, we get them ready for our analysis.

```{r}

# importing the libraries

library(tidyverse)
library(janitor)
library(lubridate)
library(skimr)
library(ggrepel)
library(ggpubr)
```

## DATASETS IMPORTATION

We import the datasets already downloaded from Kaggle.

There are 18 CSV files in the Fitbit Fitness Tracker data, capturing daily down to hours and seconds of activities on the app, however we will not be using all the datasets for this analysis.

We will focus on the most relevant datasets for our analysis, and they include:

-   Daily activity data

-   Daily sleep data

-   Hourly steps.

```{r}

# importing the data files

daily_activity <- read_csv('dailyActivity_merged.csv', show_col_types = FALSE)

daily_sleep <- read_csv('sleepDay_merged.csv', show_col_types = FALSE)

hourly_steps <-read_csv('hourlySteps_merged.csv', show_col_types = FALSE)
```

Let's take a closer look at the datasets

```{r}

# let's look at the top view of the daily activity dataset

head(daily_activity)

```

```{r}
# Checking the structure of the daily_activity dataframe

str(daily_activity)
```

There are 940 rows of data and 15 columns in the daily_activity dataset.

We notice that all the data are of type numerical including the id column, however, the ActivityDate column is character type, we will be changing this to date type later.

```{r}
# inspecting the hourly_steps data

head(hourly_steps)

str(hourly_steps)
```

```{r}
# inspecting daily sleep activity

head(daily_sleep)

str(daily_sleep)
```

We can notice that in all the datasets, the date columns are of character type which needs to be converted to date type.

Let's investigate other aspects of the data and then clean it.

Now we want to have an idea of the number of unique users of the fitbit app, this will help us deal with duplicate values that can affect our analysis.

```{r}
# how many unique user are in the datasets?

n_unique(daily_activity$Id)
n_unique(hourly_steps$Id)
n_unique(daily_sleep$Id)
```

We can see that there are 33 unique users for the daily activity and hourly steps while there are only 24 users of the daily sleep feature of the application.

### Dealing With Duplicates

Now, let's look for duplicates in the dataset and remove them.

```{r}
# looking for duplicate data in the daily_activity dataset

sum(duplicated(daily_activity))

```

```{r}
# duplicates in hourly_steps

sum(duplicated(hourly_steps))
```

```{r}
# duplicates in daily_sleep

sum(duplicated(daily_sleep))
```

There are no duplicates in the daily_activity and hourly_steps data while for the daily_sleep, there are 3 duplicates.

We will remove these duplicates

```{r}
# how many rows are in the daily_sleep dataset?

nrow(daily_sleep)
```

There are 413 rows of data in the daily_sleep dataset, and 3 out of these are duplicates, now let's remove the duplicates

## REMOVE DUPLICATES AND NAs

```{r}

daily_sleep <- daily_sleep %>% 
  distinct() %>%
  drop_na()

```

Now let's check the number of rows again

```{r}
nrow(daily_sleep)
```

Now we have 410 rows after the removal of the duplicate rows.

Let's confirm that the duplicates have actually been removed by checking for duplicates again.

```{r}
sum(duplicated(daily_sleep))
```

Duplicates have been removed from the daily_sleep data.

Now let's remove empty rows and null values from the other datasets.

```{r}
nrow(daily_activity)
nrow(hourly_steps)
```

There are 940 row of data in the daily_activity dataset and 22099 rows for the hourly_steps which captures hourly data.

Let's remove N/As and see how much data we will have.

```{r}
daily_activity <- daily_activity %>% 
  drop_na()
nrow(daily_activity)
```

There are no empty rows in daily_activity

```{r}
hourly_steps <- hourly_steps %>% 
  drop_na()
nrow(hourly_steps)
```

Also there are no null values in the hourly_steps data.

### Standardizing The Column Names

We want the datasets to have the same format in the naming of their columns so that we can easily merge them later, so we will clean and format the datasets where necessary to meet the specifications.

```{r}
daily_activity <- daily_activity %>% 
  clean_names()
head(daily_activity)
```

```{r}
head(daily_sleep)
```

We are going to format the columns of daily_sleep to lower case for uniformity.

```{r}
# we use the clean_names function from the janitor package to do this

daily_sleep <- daily_sleep %>% 
  clean_names()

head(daily_sleep)
```

And same for the hourly_steps data for consistency

```{r}
head(hourly_steps)
```

```{r}
hourly_steps <- hourly_steps %>% 
  clean_names()
head(hourly_steps)
```

### Formatting and Renaming the Date Columns

Now we are going to format the date columns of the datasets from character type to the right date type format and then rename the daily_activity and daily_sleep date columns as we will merge them later for analysis.

```{r}
# Formatting the daily-activity date column

daily_activity <- daily_activity %>% 
  rename(date = activity_date) %>% 
  mutate(date = as_date(date, format = "%m/%d/%Y"))
```

```{r}
str(daily_activity)
```

We will do same for the daily_sleep sleep_day column, note that the sleep_day column also contains time element which needs to be converted in the right format for this conversion to work.

We will be removing the time aspect because we don't need it for this analysis, this is why we are using as_date() instead of as_datetime() function.

I will assign the changes to a new variable daily_sleep1 so that if we encounter an error in the code it will not affect the main daily_sleep dataframe.

```{r}
daily_sleep1 <- daily_sleep %>% 
  rename(date = sleep_day) %>% 
  mutate(date = as_date(date, format = "%m/%d/%Y %I:%M:%S %p", tz=Sys.timezone()))
```

```{r}
daily_sleep1
```

```{r}
head(daily_activity)
head(daily_sleep1)
```

Everything worked out fine so, we will proceed to formatting the hourly_steps columns.

```{r}
head(hourly_steps)
```

```{r}
hourly_steps2 <- hourly_steps %>% 
  rename(date_time = activity_hour) %>% 
  mutate(date_time = as.POSIXct(date_time, format="%m/%d/%Y %I:%M:%S %p", tz=Sys.timezone()))
```

```{r}

# looking at the first 5 rows of the dataframe
head(hourly_steps2)

```

Everything worked fine with the renaming of the activity_hour column from character to POSIXct data type, and renaming to date_time, so let's reassign to hourly_steps.

```{r}
hourly_steps <- hourly_steps2
```

We do the same for daily_sleep

```{r}
daily_sleep <- daily_sleep1

```

Checking the reassignments

```{r}
head(daily_sleep)
head(hourly_steps)
```

Now that we have the datasets clean as we need it to be, let's merge the daily_activity and daily-sleep datasets together using the id and date columns.

```{r}
daily_activity_n_sleep <- merge(daily_activity, daily_sleep, by = c("id", "date"))

```

Let's take a look at the merged data

```{r}
head(daily_activity_n_sleep)
```

## DATA ANALYSIS

Now, we are going to analyze the data and begin to uncover insights which we hope will help the marketing team at Bellabeats take their game to a new level.

In order to try and uncover hidden trends and user behaviours of our smart device users, we need to ask some questions like.

1.  What categories of users do we have based on the data available to us?
2.  How many steps do our users take weekly?
3.  How many hours do they sleep?
4.  Which days are they most active?
5.  How frequently do they use their smart devices?
6.  Are their relationships between activities like hours of sleep vs calories or number of steps versus calories burned?
7.  How long do they use their smart devices per day?

Answering these questions will help us gain insights into how smart device users behave and the key features of the devices they appreciate the most.

These insights will then inform on app designs, marketing style and messaging, app features development and much more, which overall will deliver value to users and help grow the business for Bellabeat.

So, right away lets find out our answers:

### Categories of Users

```{r}
# We will have a look at our data to see all the variables available which will help us find our answer.

view(daily_activity_n_sleep)
```

```{r}
colnames(daily_activity_n_sleep)
```

Based on the column names, we cannot specifically identify the categories, however, we can group users based on the active distance they covered using the app.

We have the data starting from the very active distance to sedentary distance.

According to the 10000 step protocol, walking activities can be groups based on the number of steps walked into the following:

-   **Sedentary:** Less than 5,000 steps daily

-   **Low active:** About 5,000 to 7,499 steps daily

-   **Moderately active:** About 7,500 to 9,999 steps daily

-   **Active:** More than 10,000 steps daily

-   **Highly active:** More than 12,500 steps daily

This information is obtainable here, *"How Many Steps a Day Is Considered Active? (medicinenet.com)"*

So we will group app users based on this guideline

```{r}
# Let's calculate the average step of all users daily.

daily_average <- daily_activity_n_sleep %>% 
  group_by(id) %>% 
    summarise(average_steps_per_day = mean(total_steps),
    average_calories_burned_per_day = mean(calories), 
    average_sleep_per_day = mean(total_minutes_asleep)
    )

head(daily_average, 10)
```

Now that we have the average steps by each user, let's classify the user category based on the 10000 steps protocol.

```{r}
user_category <- daily_average %>% 
  mutate(user_category = case_when(
    average_steps_per_day < 5000 ~"sedentary",
    average_steps_per_day >= 5000 & average_steps_per_day < 7499 ~"low active",
    average_steps_per_day >= 7500 & average_steps_per_day < 9999 ~ "moderately active",
    average_steps_per_day >=10000 & average_steps_per_day < 12499 ~"active",
    average_steps_per_day >= 12500 ~"highly active"))

head(user_category)

```

```{r}

# to see the whole dataframe as a table and get more understanding of it.
  view(user_category)
```

Let's find the percentage of users in the categories and then visualize it using pie chart.

```{r}

user_type_percentage <- user_category %>% 
  group_by(user_category) %>% 
  summarise(user_count= n()) %>% 
  mutate(user_count_total = sum(user_count)) %>%  
  group_by(user_category) %>% 
  summarise(user_percent = user_count/user_count_total) %>% 
  mutate(labels = scales::percent(user_percent))
  
head(user_type_percentage)
```

Visualization of User Categories

```{r}
user_type_percentage %>% 
  ggplot(aes(x="", y=user_percent, fill=user_category))+
  geom_bar(stat="identity", width=1)+
  coord_polar("y", start=0)+
  theme_light()+
  theme( axis.title.x = element_blank(),
         axis.title.y= element_blank(),
         panel.border = element_blank(),
         panel.grid = element_blank(),
         axis.ticks = element_blank(),
         axis.text.x = element_blank(),
         plot.title = element_text(hjust = 0.5, size=10, face="bold"))+
  scale_fill_brewer(palette = "YlOrBr")+
  geom_text(aes(label= labels),position = position_stack(vjust = 0.5))+
  labs(title= "Categories of Users Based on Activity")
 
```

We can see that 38% of users are moderately active, there is a fair share of users who are sedentary and low-active about 21% each. 17 percent of users are very active, while only 4% are highly active users.

With this knowledge, the dev team at Bellabeat should see the importance of developing key notification features in their app and smart devices that will boost the activity levels of users. This way they will be able to convert more than 40% of smart device users from low and sedentary to active users.

The marketing team should design reward programs that can be built into the overall design of the smart devices to encourage and reward users. Perhaps competitions and leader boards would be a good idea.

### Weekday Activity Analysis

We want to analyze the activities of users and compare them by week days, this will give us insights into how the users perform on a day to day basis.

We will analyze both the activities (steps walked) and sleep habits of users on a day to day basis to uncover trends.

```{r}
# extract weekdays from the date column and create a new column for it

weekday_steps_n_sleep <- daily_activity_n_sleep %>%
  mutate(weekday = weekdays.Date(date))

# order the weekdays in the right calendar weekday sequence
weekday_steps_n_sleep$weekday <- ordered(weekday_steps_n_sleep$weekday, levels = c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday"))

# let's calculate the daily steps and sleep time and group them by weekdays.

weekday_steps_n_sleep <- weekday_steps_n_sleep %>% 
  group_by(weekday) %>% 
  summarise(avg_steps_per_day = mean(total_steps), avg_sleep_per_day = mean(total_minutes_asleep))

head(weekday_steps_n_sleep,7)
```

Let's visualize this to see if we can pick out any trends.

```{r}
weekday_steps_n_sleep %>% 
ggplot(aes(x = weekday, y= avg_steps_per_day))+
  geom_col(inherit.aes = TRUE, fill= "brown")+
  geom_hline(yintercept= 7500 )+
  labs(title= "Average Steps Per Weekday", x= "", y="")+
  theme(axis.text.x = element_text(angle=45, vjust = 0.5, hjust= 1))
```

We can see that all users walk more than 7500 steps per day all the days of the week except Sundays which is commendable, it can be assumed that users perhaps stay indoors much more on Sundays compared to other days of the week which may be the cause of the fewer steps on Sundays.

We can also see that users are most active on Saturdays, and this understandable as Saturdays are when people get more involved in fitness activities.

```{r}

weekday_steps_n_sleep %>% 
ggplot(aes(x = weekday, y= avg_sleep_per_day))+
  geom_col(inherit.aes = TRUE, fill= "orange")+
  geom_hline(yintercept= 480 )+
  labs(title= "Average Sleep Per Weekday", x= "", y="")+
  theme(axis.text.x = element_text(angle=45, vjust = 0.5, hjust= 1))
```

We can see that users get about 400 minutes (6 and a half hours) of sleep everyday of the week and slightly higher on Sundays, however this falls short of the recommended 8 hours sleep per day.

Another trend we'd like to uncover is the daily usage pattern. We want to know which times of the day that users are most active and clock-in high activities and which times of the day when they are less active.

We will use the hourly_steps data for this.

### Hourly Steps Throughout The Day

```{r}

hourly_steps_modified <- hourly_steps %>% 
  separate(date_time, into = c("date", "time"), sep= " ") %>% 
  mutate(
    date = ymd(date),
    time = if_else(time =="00:00:00", "00:00:00", time)
  )
```

I tried separating the date_time column into its separate components so we can use the time column for our analysis, however, the rows with time equal to 00:00:00 (midnight) values are giving NA values, therefore we need to replace the NA values with the same 00:00:00 values.

I tried correcting this with if_else function but it did not work.

So, let's replace them

```{r}
hourly_steps_modified <- hourly_steps_modified %>% 
  mutate(
    time = replace_na(time, "00:00:00")
  )

head(hourly_steps_modified)

```

Now, we have modified the hourly_steps data, let's find the average steps by hours and then visualize...

```{r}
hourly_steps_modified %>% 
  group_by(time) %>% 
  summarize(average_hourly_steps = round(mean(step_total),2))
```

```{r}
# visualizing the data

 hourly_steps_modified %>% 
  group_by(time) %>% 
  summarize(average_hourly_steps = mean(step_total)) %>% 
  ggplot()+
  geom_col(mapping=aes(x = time, y= average_hourly_steps, fill = average_hourly_steps))+
  labs(title= "Average Hourly Steps Per Day", x= "", y="")+
  scale_fill_gradient(low="brown", high="orange")+
  theme(axis.text.x = element_text(angle=90, vjust = 0.5, hjust= 1))
```

As we can see from the charts, users are most active between 8:00AM and 19:00PM, with peak active periods between 12:00PM - 14:00PM and 16:00PM - 19:00PM.

### Use of Smart Device

So far, we have explored user activities as it relates to time patterns, weekday patterns and user categories based on activity levels, now we want to explore usage frequency to understand the behavior around the use of smart devices.

We want to understand how often, our users use their devices. We are going to group users into categories based on their usage frequency. This can help the marketing team make informed decision when planning on market segmentation in their marketing campaigns.

We will categorize smart device users into 3:

1.  Those who use their devices between 21 to 31 days - high use
2.  Those who use their devices between 10 to 20 days - moderate use
3.  Those who use their devices between 1 to 10 days - low use

```{r}
daily_use <- daily_activity_n_sleep %>% 
  group_by(id) %>% 
  summarise(sum_of_days_used = sum(n()) )
head(daily_use)
```

Let's create our categories.

```{r}
daily_use <- daily_use %>% 
 mutate(usage = case_when(
     sum_of_days_used >= 21 & sum_of_days_used <=31 ~ "high use",
     sum_of_days_used >= 10 & sum_of_days_used <=20 ~ "moderate use",
     sum_of_days_used >= 1 & sum_of_days_used <=9 ~ "low use"
   )
 )
daily_use
```

Now, let's create a percentage column that will make visualization easy with donut chart.

```{r}
daily_use_percent <- daily_use %>%
  group_by(usage) %>% 
  summarise(count_of_usage = n()) %>% 
  mutate(total_of_usage = sum(count_of_usage)) %>% 
  group_by(usage) %>% 
  summarise(usage_percent = count_of_usage/total_of_usage) %>% 
  mutate(labels = scales::percent(usage_percent))

daily_use_percent

```

Let's plot this using a donuts chart.

```{r}

# hole size for the donut chart

h_size <- 2.5

daily_use_percent %>% 
  mutate(x = h_size) %>% 
  ggplot(mapping = aes(x = x, y = usage_percent, fill = usage)) +
  geom_col() +
  geom_text(
    aes(label = labels), position = position_stack(vjust= 0.5),
    show.legend = FALSE
    ) +
  coord_polar(theta = "y") +
  scale_fill_brewer(palette = "YlOrBr" ) +
  xlim(c(0.2, h_size + 0.5))+
  theme(panel.background = element_rect(fill = "white"),
        panel.grid = element_blank(),
        axis.title = element_blank(),
        axis.ticks = element_blank(),
        axis.text = element_blank())
```

INSIGHTS

From the chart above, we can see that 50% of smart devices users, use their devices quite frequently, which is very encouraging while 38% are low users using their smart watches just about 9 days out of a 31 days calendar. That presents a huge opportunity still for Bellabeat marketing team to explore with their marketing messaging.

As you can see, this information can help Bellabeat marketing team segment their market for more effective marketing campaigns.

### Correlation Studies

Now, we are going to be comparing some of the variables in our data to understand if there are corelations and how this can help the Bellabeat marketing team.

**Total Steps Vs Calories**

```{r}

daily_activity_n_sleep %>% 
  ggplot(mapping = aes(x= total_steps, y = calories))+
  geom_point(color = "brown", position = "jitter")+
  geom_smooth(method = "lm", color= "orange")+
  labs(title = "Daily Steps vs Calories", x= " daily steps", y= "calories" )+
  theme(plot.title = element_text(size = 12))

```

**Calories Vs Sleep Record**

```{r}

# We are installing beeswarm package to create a swarmplot for this relationship

install.packages("ggbeeswarm")

library(ggbeeswarm)

```

```{r}
# Creation of beeswarm plot

daily_activity_n_sleep %>% 
  ggplot(aes(x= total_sleep_records, y = calories, color = total_sleep_records))+
  geom_beeswarm(cex = 2)+
  scale_color_gradient(low = "brown", high= "orange")+
  labs(title= "Calories vs Sleep Record", x = "sleep record", y= "calories")+
  theme(plot.title = element_text(size = 12))
```

**Minutes Asleep vs Time in Bed**

```{r}
daily_activity_n_sleep %>% 
  ggplot(aes(y= total_minutes_asleep, x = total_time_in_bed))+
  geom_point(color= "brown")+
  geom_smooth(method= "lm", se= FALSE, color = "black")+
  labs(title= "Minutes Asleep vs Time in Bed", x = "time in bed", y= "minutes asleep")+
  theme(plot.title = element_text(size = 12))
```

### Minutes Asleep vs Calories

```{r}
daily_activity_n_sleep %>% 
  ggplot(aes(x = total_minutes_asleep, y = calories))+
  geom_point(color= "brown")+
  geom_smooth(method= "lm", se= FALSE, color = "orange")+
  labs(title= "Minutes Asleep vs Calories", x = "minutes asleep", y= "calories")+
  theme(plot.title = element_text(size = 12))

```

```{r}

# Let's assemble all the plots in one place.

ggarrange(
  ggplot(daily_activity_n_sleep, aes(x= total_steps, y = calories))+
    geom_point(color = "brown", position = "jitter")+
    geom_smooth(method = "lm", color= "orange")+
    labs(title = "Daily Steps vs Calories", x= " daily steps", y= "calories" )+
    theme(plot.title = element_text(size = 12)),

  ggplot(daily_activity_n_sleep, aes(x = total_minutes_asleep, y = calories))+
    geom_point(color= "brown")+
    geom_smooth(method= "lm", se= FALSE, color = "orange")+
    labs(title= "Minutes Asleep vs Calories", x = "minutes asleep", y= "calories")+
    theme(plot.title = element_text(size = 12)),

  ggplot(daily_activity_n_sleep, aes(x= total_sleep_records, y = calories, color = total_sleep_records))+
    geom_beeswarm(cex = 2)+
    scale_color_gradient(low = "brown", high= "orange")+
    labs(title= "Sleep Record vs Calories", x = "sleep record", y= "calories")+
    theme(plot.title = element_text(size = 12)),

  ggplot(daily_activity_n_sleep, aes(x = total_time_in_bed, y= total_minutes_asleep))+
    geom_point(color= "brown")+
    geom_smooth(method= "lm", se= FALSE, color = "black")+
    labs(title= "Minutes Asleep vs Time in Bed", x = "time in bed", y= "minutes asleep")+
    theme(plot.title = element_text(size = 12))
)

```

### Insights

From the charts above, we begin to see some patterns.

1.  Daily Steps vs Calories

    We can see that there's a strong positive correlation between the number of steps a user walks in a day and the amount of calories burned which is expected and why walking daily is an open secret for losing weight and keeping in shape.

2.  Minutes Asleep vs Calories

    We cannot see a clear correlation between minutes asleep and calories burned. However, we can see that there's a slight negative correlation. Users who sleep less minutes, especially below 200 minutes a day seem to burn more calories but as the quality of sleep increases, the data becomes mixed up, therefore we cannot say that the calories burned is due to sleeping less, it could be from the stress associated with not sleeping enough.

3.  Sleep Record vs Calories

    We can see from this chart that most of our users sleep once a day, and just a handful sleep twice and 3 times a day.

    There is no correlation between the number of times slept and calories burned, however from the chart we can see that those who sleep 3 times a day burn less calories that those who sleep once a day and twice daily.

4.  Time in Bed vs Minutes Asleep

```         
We can see a strong positive correlation between time in bed and minutes asleep. It simply means that the more time you stay in bed the more likely sleep you would tend to sleep.
```

These insights can benefit the marketing team at Bellabeat in many ways especially in creating advertising communication that showcases the benefits of wearing Bellabeat smartwatches.

## CONCLUSION AND RECOMMENDATION

The Bellabeat team now have an exciting basket of insights about the users of smart devices from their daily habits to their attitude around usage of smart devices.

We can see that there is a lot of opportunities to explore both for the marketing and product team in using these uncovered insights to improve the product as well the marketing campaigns at BellaBeat.
